---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Heading 1

## Heading 2

### Heading 3 

-----

This is a test vignette to demonstrate the purpose/use of our package.

*****

* Bulleted list
* Item 2
    * Nested bullet need a 4-space indent.
    * Item 2b.
    
* It's possible to put multiple paragraphs of text in a list item.

    But to do that, the second and subsequent paragraphs must be
    indented by four or more spaces. It looks better if the first 
    bullet is also indented.
    
1. Item 1
1. Item 2
1. Items are numbered automatically, even though they all start with 1.

1. Item 1.
    * Item a
    * Item b
1. Item 2.

Definition
    : a statement of the exact meaning of a word, especially in a dictionary.
List
    : a number of connected items or names written or printed consecutively, typically one below the other.
    : barriers enclosing an area for a jousting tournament.
    
_italic_ or *italic*

__bold__ or **bold**

[link text] (destination)

[my website] (https://www.heililowman.com)

<http://this-is-a-raw-url.com>

pipe table:

| Right | Left | Default | Center |
|------:|:-----|---------|:------:|
|   12  |  12  |    12   |    12  |
|  123  |  123 |   123   |   123  |
|    1  |    1 |     1   |     1  |

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(celinepkg)
```

```
# A comment
add <- function(a, b) a + b
```

```c
int add(int a, int b) {
return a + b;
}
```

```{r code}

# Add two numbers together
add <- function(a, b) a + b
add(10, 20)

```

Some additional options in the {r} heading:

eval = FALSE prevents evaluation of the code

echo = FALSE does not print the code input

results = "hide" does not print the code output.

warning = FALSE and message = FALSE suppress displays of warnings and messages.

error = TRUE captures errors and shows them inline

fig.show = "hold" puts all figures at the end of the code block.

fig.width = 5 and fig.height = 5 set the width and height of figures (in inches).

